### 2013-07-29 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
cleaning up some figures in the spn section

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/driven_re500_forcing.pdf}
  \end{center}
  \caption{\textbf{Lid driven cavity forcing terms as a function of
      Newton iteration for the 500 Reynolds number case.} \textit{Once
      the region of fast quadratic convergence is reached, MCSA
      forcing terms were much larger.}}
  \label{fig:driven_re500_forcing}
\end{figure}

@@

Unlike the lid driven cavity benchmark, the extra linear solver
iterations are not due to the smaller forcing terms but are rather
truly a function of the ill-conditioning of the Jacobian matrices
produced at each Newton step. We see this by comparing the results at
Reynolds numbers of 400 where FANM outperformed Newton-Krylov and 500
where Newton-Krylov outperformed FANM. Linear iterations as a function
of nonlinear iteration given in Figure~\ref{fig:step_re400_iters} and
the forcing term as a function of nonlinear iteration given in
Figure~\ref{fig:step_re400_forcing} for the 400 Reynolds number case
and the same data is given in Figure~\ref{fig:step_re500_iters} and
Figure~\ref{fig:step_re500_forcing} for the 500 Reynolds number
case. For both cases, FANM always has larger forcing terms and should
therefore use fewer MCSA iterations at each Newton step to converge
the linear model. This is indeed the case for the 400 Reynolds number
case where the linear model is better conditioned and FANM used fewer
total linear solver iterations to converge the nonlinear
residual. However, at a Reynolds number of 500 FANM has larger forcing
terms but requires many more MCSA iterations to converge the last 2
Newton steps. Therefore, these extra iterations in this case must come
from ill-conditioning.

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/driven_re500_forcing.pdf}
  \end{center}
  \caption{\textbf{Lid driven cavity forcing terms as a function of
      Newton iteration for the 500 Reynolds number case.} \textit{Once
      the region of fast quadratic convergence is reached, MCSA
      forcing terms were much smaller.}}
  \label{fig:driven_re500_forcing}
\end{figure}

@@

Unlike the lid driven cavity benchmark, the extra linear solver
iterations are not due to the smaller forcing terms but are rather
truly a function of the ill-conditioning of the Jacobian matrices
produced at each Newton step. We see this by comparing the results at
Reynolds numbers of 400 where FANM outperformed Newton-Krylov and 500
where Newton-Krylov outperformed FANM. Linear iterations as a function
of nonlinear iteration given in Figure~\ref{fig:step_re400_iters} and
the forcing term as a function of nonlinear iteration given in
Figure~\ref{fig:step_re400_forcing} for the 400 Reynolds number case
and the same data is given in Figure~\ref{fig:step_re500_iters} and
Figure~\ref{fig:step_re500_forcing} for the 500 Reynolds number
case. For both cases, FANM always has larger forcing terms and should
therefore use fewer MCSA iterations at each Newton step to converge
the linear model if the iterative performance is comparable. This is
indeed the case for the 400 Reynolds number case where the linear
model is better conditioned and FANM used fewer total linear solver
iterations to converge the nonlinear residual. However, at a Reynolds
number of 500 FANM has larger forcing terms but requires many more
MCSA iterations to converge the last 2 Newton steps. Therefore, these
extra iterations in this case must come from ill-conditioning.
